Determinism, Complexity, and Predictability in Computer Performance

### 2014-01-10 pecomplexity.tex
add two new images

>>>>

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\textwidth]{figs/SVD_wwpe}
  \caption{The weighted permutation entropy of one run of SVD. The gray bands
    are regions where the window overlaps regimes. The window size used is
    $5,000 \times 100,000$ instructions and the word length is $4$.}
  \label{fig:wwpe}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\textwidth]{figs/prediction_vs_entropy}
  \caption{The improvement of LMA over na\"{i}ve vs weighted permutation entropy.
  For each of these, the word length used is $5$.}
  \label{fig:pred_vs_ent}
\end{figure}
